### 2015-02-26 ThesisJo/introduction.tex
la2pdf commit - 2015:02:26	17:29:41	(Thu26.Feb)
la2pdf commit - 2015:02:26	18:05:17	(Thu26.Feb)
la2pdf commit - 2015:02:26	19:38:45	(Thu26.Feb)
la2pdf commit - 2015:02:26	20:09:33	(Thu26.Feb)

\chapter{Introduction}

@@

>>>>

\chapter{Background}

\section{Coordinate System}

\begin{figure}[th]
\graphicsAI[width=\linewidth]{gfx/geometry.svg}
\caption{The coordinate system used throughout the thesis.}\label{geometry}
\end{figure}

In this thesis we will relate all geometrical interpretations to the euclidean, spherical coordinate system shown in \Fig{geometry}. When assessing the imaging performance of a sonar its origin will be in the center of the array, but when assessing scenes its origin will be in the center of the image. A unit length vector $\vec u$ can be written as:
%
\begin{align*}
\vec u =
\begin{bmatrix}
\sin\theta \cos\phi \\
\sin\theta \sin\phi \\
\cos\theta
\end{bmatrix}
\end{align*}
%

@@

The wave equation is the single most important equation governing a wave's propagation through a medium. When the medium is loss-less it can be expressed as:
